Many-core applications to online track reconstruction in HEP experiments

### 2013-10-16 papers/2013/CHEP/paper.tex
start changing abstract to focus on what's new

\begin{abstract}
  One of the most important issues facing particle physics experiments
  at hadron colliders is real-time selection of interesting events for
  offline storage.  Collision frequencies do not allow all events to
  be written to tape for offline analysis, and in most cases, only a
  small fraction can be saved.  Typical trigger systems use commercial
  computers in the final stage of processing. Much of the effort is
  focused on understanding the latency for trigger systems. In this
  paper we describe updates to a previous study of latencies in GPU
  for potential trigger applications, where we measured the latency to
  transfer data to/from the GPU, exploring the timing of different I/O
  technologies on different GPU models.  Those studies, where a
  simplified track fitting algorithm was parallelized and run on a
  GPU, show that latencies of few tens of microseconds can be achieved
  to transfer and process packets of 4 kB of data, combining the
  modern Infiniband data transfer technology with direct access to GPU
  memory allowed by NVIDIA GPUDirect utilities.  We now have expanded
  our latency studies to include other multi-core systems (Intel Xeon
  Phi in addition to NVIDIA GPUs). We also discuss the implementation
  of a scaled-up version of the algorithm used at CDF for online track
  reconstruction - the SVT algorithm - as a realistic test-case for
  low-latency trigger systems using new computing architectures for
  LHC experiment.

>>>>

\begin{abstract}
  In this paper we describe updates to a previous study of latencies
  in GPU for potential trigger applications, where we measured the
  latency to transfer data to/from the GPU, exploring the timing of
  different I/O technologies on different GPU models.  Those studies,
  where a simplified track fitting algorithm was parallelized and run
  on a GPU, show that latencies of few tens of microseconds can be
  achieved to transfer and process packets of 4 kB of data, combining
  the modern Infiniband data transfer technology with direct access to
  GPU memory allowed by NVIDIA GPUDirect utilities.  We now have
  expanded our latency studies to include other multi-core systems
  (Intel Xeon Phi in addition to NVIDIA GPUs). We also discuss the
  implementation of a scaled-up version of the algorithm used at CDF
  for online track reconstruction - the SVT algorithm - as a realistic
  test-case for low-latency trigger systems using new computing
  architectures for LHC experiment.
